GDPR: Is non-compliance profitable for Meta Platforms, Inc.?

### 2023-06-11 docs/research/LaTeX/research.tex
Fix bugs with image placement and references

\documentclass[12pt, a4paper]{article}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{url}
\usepackage{cite}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\graphicspath{{images/}}
\title{GDPR: Is non-compliance profitable for Meta Platforms, Inc.?}
\author{Stoyan L. Kostadinov}
\date{June 2023}
\begin{document}
\maketitle

@@

\begin{itemize}
    \item Articles published in English
    \item Articles published between 2018 and 2023
    \item Articles that discuss GDPR
    \item Articles that discuss Meta Platforms, Inc.
    \item Data between 2018 and 2023
\end{itemize}

@@

\begin{itemize}
    \item Articles published in languages other than English
    \item Articles published before 2018
    \item Articles that do not discuss GDPR
    \item Articles that do not discuss Meta Platforms, Inc.
    \item Articles that discuss about ethics
    \item Data before 2018
\end{itemize}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{monetarial-amount-of-gdpr-fines}
    \caption{Monetarial amount of fines issued to Meta Platforms, Inc.(in
    millions of
    \$)\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
    \label{fig:amount-of-gdpr-fines}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{violations-by-article}
    \caption{Number of violations by GDPR
    article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
    \label{fig:violations-by-article}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{net-income}
    \caption{Net Income of Meta Platforms, Inc.(in billions of
    \$)\cite{2023q1,2020q4,2020q3,2020q2,2020q1,2019q4,2019q3,2019q2,2019q1,2018q4,2018q3,2018q2}}
    \label{fig:net-income}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{revenue}
    \caption{Revenue of Meta Platforms, Inc.(in billions of
    \$)\cite{2023q1,2020q4,2020q3,2020q2,2020q1,2019q4,2019q3,2019q2,2019q1,2018q4,2018q3,2018q2}}
    \label{fig:revenue}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{family-revenue-per-person}
    \caption{Family Revenue per Person (FRP) of Meta Platforms,
    Inc.\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:family-revenue-per-person}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{advertising-revenue-by-user-geography}
    \caption{Advertising Revenue by User Geography of Meta Platforms, Inc.(in
    billions of \$)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:advertising-revenue-by-user-geography}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{family-dap}
    \caption{Family Daily Active People (FDAP) of Meta Platforms, Inc.(in
    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:family-dap}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{family-map}
    \caption{Family Monthly Active People (FMAP) of Meta Platforms, Inc.(in
    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:family-map}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{facebook-dau}
    \caption{Facebook Daily Active Users (FDAU) of Meta Platforms, Inc.(in
    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:facebook-dau}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.00\textwidth]{facebook-mau}
    \caption{Facebook Monthly Active Users (FMAU) of Meta Platforms, Inc.(in
    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:facebook-mau}
\end{figure}

>>>>

\documentclass[12pt, a4paper]{article}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\usepackage{cite}
\usepackage{float}
\usepackage[font=footnotesize,labelfont=bf]{caption}
\graphicspath{{images/}}
\title{GDPR: Is non-compliance profitable for Meta Platforms, Inc.?}
\author{Stoyan L. Kostadinov}
\date{June 2023}
\begin{document}
\maketitle

@@

\begin{itemize}
    \item Articles published in English
    \item Articles published after 2010
    \item Data about GDPR fines
    \item Data about \textit{Meta Platforms, Inc.} financials
    \item Data between 2018 and 2023
\end{itemize}

@@

\begin{itemize}
    \item Articles published in languages other than English
    \item Articles published before 2010
    \item Data that is not about GDPR fines
    \item Data that is not about \textit{Meta Platforms, Inc.} financials
    \item Data before 2018
\end{itemize}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{monetarial-amount-of-gdpr-fines}
    \caption{Monetarial amount of fines issued to Meta Platforms, Inc.(in
    millions of
    \$)\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
    \label{fig:amount-of-gdpr-fines}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{violations-by-article}
    \caption{Number of violations by GDPR
    article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
    \label{fig:violations-by-article}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{net-income}
    \caption{Net Income of Meta Platforms, Inc.(in billions of
    \$)\cite{2023q1,2020q4,2020q3,2020q2,2020q1,2019q4,2019q3,2019q2,2019q1,2018q4,2018q3,2018q2}}
    \label{fig:net-income}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{revenue}
    \caption{Revenue of Meta Platforms, Inc.(in billions of
    \$)\cite{2023q1,2020q4,2020q3,2020q2,2020q1,2019q4,2019q3,2019q2,2019q1,2018q4,2018q3,2018q2}}
    \label{fig:revenue}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{family-revenue-per-person}
    \caption{Family Revenue per Person (FRP) of Meta Platforms,
    Inc.\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:family-revenue-per-person}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{advertising-revenue-by-user-geography}
    \caption{Advertising Revenue by User Geography of Meta Platforms, Inc.(in
    billions of \$)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:advertising-revenue-by-user-geography}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{family-dap}
    \caption{Family Daily Active People (FDAP) of Meta Platforms, Inc.(in
    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:family-dap}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{family-map}
    \caption{Family Monthly Active People (FMAP) of Meta Platforms, Inc.(in
    billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:family-map}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{facebook-dau}
    \caption{Facebook Daily Active Users (FDAU) by Geographical Location of Meta
    Platforms, Inc.(in billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:facebook-dau}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{facebook-mau}
    \caption{Facebook Monthly Active Users (FMAU) by Geographical Location of
    Meta Platforms, Inc.(in billions)\cite{2023q1,2021q2Slides,2019q4Slides}}
    \label{fig:facebook-mau}
\end{figure}
